\documentclass{scrartcl}

\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

\usepackage{amsmath}

\title{Agile Development Essay Question: How Can the Scrum Master Help Improve Workflow of a Project?}

\subtitle{COMP150 - Agile Development Practice}


\author{1603294}

\begin{document}

\maketitle

\abstract{This essay will be on the scrum master and how they can help improve the workflow of a project in the agile development practises. The modern era is constantly advancing technology in leaps and bounds so development teams must come up with better ways of developing software than the original linear/waterfall method that relied on the work being fully planned out before beginning any work. As of late a new practise has arisen that greatly improves the workflow of a project, The Agile Development Practise.}

\section{Introduction}

The Agile Development Practises work on a day to day planning then working basis in sessions such as scrums. These scrums are set up so that all the work done in the previous day is reviewed and then if anything needs changing the scrum master adjusts the work plan for that day to maximise the scrums overall output. The scrum master is the one in charge of maintaining the course of the scrums and making sure that there is nothing blocking the development process. The scrum master also gets information from the product owner that includes input from end-users, stakeholders and customers.

\section{1. Shared Leadership in a scrum}

The Agile Development Practise greatly revolves around shared leadership and has a huge emphasis on teamwork and information sharing. The leadership of the team is shared between each member \cite{moe2009understanding} meaning no one member has complete control over who is allocated what to work on. This is the main aspect of the agile method known as a Scrum \cite{moe2009understanding}. A scrum consists of multiple blocks of work know as sprints. The size of a sprint can differ depending on the size of the team, the size of the project and the experience of the team, however sprints are usually 3 weeks long.

A Scrum Master has a very important role within the Agile Development Practises. It's their job to hold daily stand-up meetings and to make sure all work is being progressed through steadily without fault. The scrum master will also address if someone is taking on to many projects at once and sort out how that can be amended. The scrum master however is not the overall boss of the project.

The Agile Manifesto suggests that companies should "Build projects around motivated individuals, give them the environment and support they need and trust them to get the job done." \cite{fowler2001agile}. This would imply that while it is important to create a team that has a lot of motivation for the project. This is especially true within game development. If a team has been assembled and is not motivated to work on the project then the game will ultimately be a failure.

\section{Conclusion}

In the papers and slideshows read for this project most if not all stated how important good teamwork and strong management can help improve both the workflow of a project and the quality of a project. All of the sources stated how it was important for the team not to be impeded while working on a project. As it's the scrum masters job to get rid of all blockers impeding the process of the team this makes them vital for the continuation of a project.

\bibliographystyle{ieeetran}
\bibliography{references}

\end{document}
